
```{r read-course-data, include = FALSE}
pathway <- "~/Desktop/teaching/courses-taught.csv"
teaching <- read.table(pathway, sep = ",", header = TRUE)
teaching <- teaching |> 
  dplyr::distinct(course.abbr, .keep_all = TRUE) |> 
  dplyr::arrange(course.title)
```



## University of Vienna

**Methods in Cognitive Biology (Statistics in R Module): 300349**  

[Methods in Cognitive Biology website](https://dancmann.github.io/methods-in-cognitive-bio-website/index.html)

I made this website as part of teaching a Methods in Cognitive Biology course. 
I taught the statistics and programming sections. 

## Brooklyn College
```{r include=FALSE}
i <- 1
```

**`r teaching$course.title[i]`**: `r teaching$course.abbr[i]`  
<ins>Course Description</ins>:&nbsp;  `r teaching$description[i]` `r i=i+1`  

**`r teaching$course.title[i]`**: `r teaching$course.abbr[i]`  
<ins>Course Description</ins>:&nbsp;  `r teaching$description[i]` `r i=i+1`

**`r teaching$course.title[i]`**: `r teaching$course.abbr[i]`  
<ins>Course Description</ins>:&nbsp;  `r teaching$description[i]` `r i=i+1`

**`r teaching$course.title[i]`**: `r teaching$course.abbr[i]`  
<ins>Course Description</ins>:&nbsp;  `r teaching$description[i]` `r i=i+1`

**`r teaching$course.title[i]`**: `r teaching$course.abbr[i]`  
<ins>Course Description</ins>:&nbsp;  `r teaching$description[i]` `r i=i+1`

**`r teaching$course.title[i]`**: `r teaching$course.abbr[i]`  
<ins>Course Description</ins>:&nbsp;  `r teaching$description[i]` `r i=i+1`

**`r teaching$course.title[i]`**: `r teaching$course.abbr[i]`  
<ins>Course Description</ins>:&nbsp;  `r teaching$description[i]` `r i=i+1`

**`r teaching$course.title[i]`**: `r teaching$course.abbr[i]`  
<ins>Course Description</ins>:&nbsp;  `r teaching$description[i]` `r i=i+1`